A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-07 docs/methods/erosion_methods.tex
fixed bibliography

For these porous network simulations, it is essential to resolve the
nonlocal effects between the different bodies.  BIEs naturally resolve
these interactions, and they have been used extensively to simulate
viscous fluids in complex geometries, including porous media
flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}.  Common challenges
of a BIE formulation include developing efficient preconditioners for
the discretized system and numerical difficulties associated with nearly
touching bodies. In this work, we consider geometries requiring
$\mathcal{O}(100)$ GMRES iterations, so that preconditioners are not
necessary. In future work, we will address mobile bodies for which near
contacts may necessitate preconditoners~\cite{qua-bir2015a,
qua-cou-dar2018, cou-pou-dar2017}. Similarly, near-singular schemes will
not be necessary due to the fact that the spacing between receding
bodies of fixed position always grows in time. Again, the future
consideration of mobile bodies may necessitate near-singular
schemes~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015,
hel-oja2008a, bea-lai2001}.

>>>>

For these porous network simulations, it is essential to resolve the
nonlocal effects between the different bodies.  BIEs naturally resolve
these interactions, and they have been used extensively to simulate
viscous fluids in complex geometries, including porous media
flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.  Common challenges
of a BIE formulation include developing efficient preconditioners for
the discretized system and numerical difficulties associated with nearly
touching bodies. In this work, we consider geometries requiring
$\mathcal{O}(100)$ GMRES iterations, so that preconditioners are not
necessary. In future work, we will address mobile bodies for which near
contacts may necessitate preconditoners~\cite{qua-bir2015a,
qua-cou-dar2018, cou-pou-dar2017}. Similarly, near-singular schemes will
not be necessary due to the fact that the spacing between receding
bodies of fixed position always grows in time. Again, the future
consideration of mobile bodies may necessitate near-singular
schemes~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015,
hel-oja2008a, bea-lai2001}.
